---
title: "CourseNotes_Week2 Expressions and Environments"
output: html_notebook
---


## Working with Expressions and Environments in R


### Expressions

Expressions are encapsulated operations that can be executed by R. This may sound complicated, but using expressions allows you manipulate code with code! You can create an expression using thequote() function. For that function’s argument, just type whatever you would normally type into the R console. For example:

```{r}

two_plus_two <- quote(2 + 2)
two_plus_two
```

You can execute this expressions using the eval() function:


```{r}
eval(two_plus_two)
```

You might encounter R code that is stored as a string that you want to evaluate with eval(). You can use parse() to transform a string into an expression:



```{r}
tpt_string <- "2 + 2"
tpt_expression <- parse(text = tpt_string)
eval(tpt_expression)
```

[1] 4
You can reverse this process and transform an expression into a string using deparse():


```{r}
deparse(two_plus_two)
```

[1] "2 + 2"
One interesting feature about expressions is that you can access and modify their contents like you a list(). This means that you can change the values in an expression, or even the function being executed in the expression before it is evaluated:


```{r}
sum_expr <- quote(sum(1, 5))
eval(sum_expr)
```

[1] 6
sum_expr[[1]]
sum
sum_expr[[2]]
[1] 1
sum_expr[[3]]
[1] 5
```{r}
sum_expr[[1]] <- quote(paste0)
sum_expr[[2]] <- quote(4)
sum_expr[[3]] <- quote(6)
eval(sum_expr)
```

You can compose expressions using the call() function. The first argument is a string containing the name of a function, followed by the arguments that will be provided to that function.


```{r}
sum_40_50_expr <- call("sum", 40, 50)
sum_40_50_expr
sum(40, 50)
eval(sum_40_50_expr)
```

You can capture the the expression an R user typed into the R console when they executed a function by including match.call() in the function the user executed:

```{r}
return_expression <- function(...){
  match.call()
}
return_expression(2, col = "blue", FALSE)
return_expression(2, col = "blue", FALSE)
```

You could of course then manipulate this expression inside of the function you’re writing. The example below first uses match.call()to capture the expression that the user entered. The first argument of the function is then extracted and evaluated. If the first expressions is a number, then a string is returned describing the first argument, otherwise the string "The first argument is not numeric." is returned.

```{r}
first_arg <- function(...){
  expr <- match.call()
  first_arg_expr <- expr[[2]]
  first_arg <- eval(first_arg_expr)
  if(is.numeric(first_arg)){
    paste("The first argument is", first_arg)
  } else {
    "The first argument is not numeric."
  }
}
first_arg(2, 4, "seven", FALSE)
```


```{r}
first_arg("two", 4, "seven", FALSE)
```

Expressions are a powerful tool for writing R programs that can manipulate other R programs.



### Environments

Environments are data structures in R that have special properties with regard to their role in how R code is executed and how memory in R is organized. You may not realize it but you’re probably already familiar with one environment called the global environment. Environments formalize relationships between variable names and values. When you enter x <- 55 into the R console what you’re saying is: assign the value of 55 to a variable called x, and store this assignment in the global environment. The global environment is therefore where most R users do most of their programming and analysis.

You can create a new environment using new.env(). You can assign variables in that environment in a similar way to assigning a named element of a list, or you can use assign(). You can retrieve the value of a variable just like you would retrieve the named element of a list, or you can use get(). Notice that assign() and get() are opposites:


```{r}
my_new_env <- new.env()
my_new_env$x <- 4
my_new_env$x
```

[1] 4
```{r}
assign("y", 9, envir = my_new_env)
get("y", envir = my_new_env)
```

```{r}
my_new_env$y
```

You can get all of the variable names that have been assigned in an environment using ls(), you can remove an association between a variable name and a value using rm(), and you can check if a variable name has been assigned in an environment using exists():


```{r}
ls(my_new_env)
```


```{r}
rm(y, envir = my_new_env)
exists("y", envir = my_new_env)
```


```{r}
exists("x", envir = my_new_env)
```


```{r}
my_new_env$x
```


```{r}
my_new_env$y
```

Environments are organized in parent/child relationships such that every environment keeps track of its parent, but parents are unaware of which environments are their children. Usually the relationships between environments is not something you should try to directly control. You can see the parents of the global environment using thesearch() function:


```{r}
search()
```

 [1] ".GlobalEnv"             "package:magrittr"      
 [3] "package:tidyr"          "package:microbenchmark"
 [5] "package:purrr"          "package:dplyr"         
 [7] "package:readr"          "package:stats"         
 [9] "package:graphics"       "package:grDevices"     
[11] "package:utils"          "package:datasets"      
[13] "Autoloads"              "package:base"          

As you can see package:magrittr is the parent of .GlobalEnv, and package:tidyr is parent of package:magrittr, and so on. In general the parent of .GlobalEnv is always the last package that was loaded usinglibrary(). Notice that after I load the ggplot2 package, that package becomes the parent of .GlobalEnv:


### Execution Environments

Although there may be several cases where you need to create a new environment using new.env(), you will more often create new environments whenever you execute functions. An execution environment is an environment that exists temporarily within the scope of a function that is being executed. For example if we have the following code:


```{r}
x <- 10
my_func <- function(){
  x <- 5
  return(x)
}
my_func()
```

What do you think will be the result of my_func()? Make your guess and then take a look at the executed code below:


```{r}
x <- 10
my_func <- function(){
  x <- 5
  return(x)
}
my_func()
```


So what exactly is happening above? First the name x is being assigned the value 10 in the global environment. Then the namemy_func is being assigned the value of the function function(){x <- 5};return(x)} in the global environment. When my_func() is executed, a new environment is created called the execution environment which only exists while my_func() is running. Inside of the execution environment the name x is assigned the value 5. Whenreturn() is executed it looks first in the execution environment for a value that is assigned to x. Then the value 5 is returned. In contrast to the situation above, take a look at this variation:


```{r}
x <- 10
another_func <- function(){
  return(x)
}
another_func()
```

In this situation the execution environment inside of another_func()does not contain an assignment for the name x, so R looks for an assignment in the parent environment of the execution environment which is the global environment. Since x is assigned the value 10 in the global environment 10 is returned.

After seeing the cases above you may be curious if it’s possible for an execution environment to manipulate the global environment. You’re already familiar with the assignment operator <-, however you should also be aware that there’s another assignment operator called the complex assignment operator which looks like <<-. You can use the complex assignment operator to re-assign or even create name-value bindings in the global environment from within an execution environment. In this first example, the function assign1() will change the value associated with the name x:



```{r}
x <- 10
x
```

```{r}
assign1 <- function(){
  x <<- "Wow!"
}
assign1()
x
```

You can see that the value associated with x has been changed from 10 to "Wow!" in the global environment. You can also use <<- to assign names to values that have not been yet been defined in the global environment from inside a function:


```{r}
a_variable_name
```

```{r}
exists("a_variable_name")
```


```{r}
assign2 <- function(){
  a_variable_name <<- "Magic!"
}
assign2()
exists("a_variable_name")
```

```{r}
a_variable_name
```


If you want to see a case for using <<- in action, see the section of this book about functional programming and the discussion there about memoization.

