---
title: "RProgramming_Course1Assignment"
author: "Frank Fichtenmueller"
date: "2 November 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This is the Solution to the Reading and Summarizing Data Quiz
```{r}
library(readr)
library(dplyr)
library(tidyr)
library(readxl)
```

Loading the dataset
```{r}
# Setting the route directory
getwd()
setwd("D:/AAA_ProgrammingFiles/AAA_Learning/Coursera_SoftwareDevInR/RProgrammingEnv/Week4")

# Loading the .csv file
if(!exists("daily_spec")){
    daily_spec <- read_csv("./data/daily_SPEC_2014.csv.bz2",col_types = cols(`State Code` = col_number(), `County Code` = col_number(), `Site Num` = col_number(), `Parameter Code` = col_number() ),n_max = 20)
    daily_spec <- read_csv("./data/daily_SPEC_2014.csv.bz2")
}
read_s
# Loading the Excel file
aqs_sites <- read_excel("./data/aqs_sites.xlsx")
str(daily_spec)
```
```{r}
spec()
```

Checking the column attributes
```{r}
unique(daily_spec$`Parameter Name`)
```



Getting a first glimpse at the data and refining the dataimport


```{r}
#Identifying the Parameter Code for "PM2.5"
names(daily_spec)
  
```


```{r}
unique(daily_spec$`Parameter Name`)
str(daily_spec$`Pollutant Standard`)
filter(daily_spec, daily_spec$`Parameter Name` == contains("LC"))
```


Creating subsamples to check for joining:
```{r}
# Create subsamples
sites_m <- slice(aqs_sites,1:20)
spec_m <- slice(daily_spec, 1:20)

# Try for best join
inner_join(sites_m, spec_m, by="State Code")
```



## 1.Question

What is average Sample.Value for "Bromine PM2.5 LC" in the state of Wisconsin in this dataset?
```{r}
daily_spec %>% 
  group_by(`State Code`) %>% 
  filter(`Parameter Name` == "Bromine PM2.5 LC", `State Name` == "Wisconsin") %>% 
  summarise( avg_pollutant = mean(`Arithmetic Mean`, na.rm=TRUE))
```

## 2.Question
Calculate the average of each chemical constituent across all states, monitoring sites and all time points.

```{r}
daily_spec %>% 
  group_by(`Parameter Name`) %>% 
  filter(grepl("LC", `Parameter Name`)) %>% 
  summarise(avg_concentration = mean(`Arithmetic Mean`, na.rm=TRUE)) %>% 
  arrange(desc(avg_concentration))
```

## Question 3
Which monitoring site has the highest average level of "Sulfate PM2.5 LC" across all time?

Indicate the state code, county code, and site number.
```{r}
daily_spec %>% 
  select(`State Code`, `County Code`, `Site Number`, `Arithmetic Mean`, `Parameter Name`) %>% 
  group_by(`State Code`, `County Code`, `Site Number`) %>% 
  filter(`Parameter Name` == "Sulfate PM2.5 LC") %>% 
  summarise(avg_concentration = mean(`Arithmetic Mean`, na.rm = TRUE)) %>% 
  arrange(desc(avg_concentration))
```

Find the mean concentration for all pollutants over time in one City
```{r}
get_means <- function(cities, pollutant) {
  daily_spec %>% 
      filter(`City Name` %in% cities, `Parameter Name` == pollutant) %>% 
      group_by(`City Name`, `Parameter Name`) %>% 
      filter(grepl("LC", `Parameter Name` )) %>% 
      summarise(avg_concentration = mean(`Arithmetic Mean`))
}

get_means("Boston", "OC PM2.5 LC TOR")
```


## Question 4
What is the absolute difference in the average levels of "EC PM2.5 LC TOR" between the states California and Arizona, across all time and all monitoring sites?
```{r}
# Calculating the Pollutatnt Means for California, Arizona
concen <- daily_spec %>%
  filter(`State Name` %in% c("California", "Arizona"), `Parameter Name`=="EC PM2.5 LC TOR") %>% 
  group_by(`State Name`) %>% 
  summarise(avg_concentration = mean(`Arithmetic Mean`))

# Calculating the absolute difference
abs(concen[,2][1,1] - concen[,2][2,1])

```

## Question 5
What is the median level of "OC PM2.5 LC TOR" in the western United States, across all time? Define western as any monitoring location that has a Longitude LESS THAN -100.
```{r}
daily_spec %>% 
  filter(Longitude < -100, `Parameter Name` == "OC PM2.5 LC TOR" ) %>% 
  summarise(med_level = median(`Arithmetic Mean`))
```

## Question 6

Use the readxl package to read the file aqs_sites.xlsx into R (you may need to install the package first). This file contains metadata about each of the monitoring sites in the EPA's monitoring system. In particular, the "Land Use" and "Location Setting" variables contain information about what kinds of areas the monitors are located in (i.e. "residential" vs. "forest").

```{r}
str(aqs_sites)
```

Change the column classes of a subst of columns 
```{r}
daily_spec <- mutate_each(daily_spec, funs(as.numeric), 1:3)
```

```{r}
sapply(daily_spec, class)
sapply(aqs_sites, class)
```

Calculating the frequency
```{r}
table(aqs_sites$`Land Use`)
```

```{r}
aqs_sites %>% 
  filter(`Land Use` == "RESIDENTIAL", `Location Setting` =="SUBURBAN") %>% 
  summarise(n())
```


## Question 7
What is the median level of "EC PM2.5 LC TOR" amongst monitoring sites that are labelled as both "RESIDENTIAL" and "SUBURBAN" in the eastern U.S., where eastern is defined as Longitude greater than or equal to -100?

In order to join the tables we have to set the codes the same
```{r}
# Check if the identifiers are the same
names(daily_spec)[1:5] == names(aqs_sites)[1:5]


str(daily_spec)
str(aqs_sites)
```

So we can now join on (State, County, SideId)
```{r}
joined_tbl <- inner_join(aqs_sites, daily_spec)
summary(joined_tbl$`Arithmetic Mean`)

joined_tbl %>% 
  group_by(`State Code`, `County Code`,`Parameter Name`) %>% 
  summarise(avg_concentration = mean(`Arithmetic Mean`)) %>% 
  arrange(desc(avg_concentration))

unique(joined_tbl$`Parameter Name`)
```

Calculating the median level
```{r}
joined_tbl %>% 
  group_by(`State Code`, `County Code`, `Site Number`, `Parameter Name`) %>% 
  filter(`Location Setting`== "SUBURBAN", `Land Use`=="RESIDENTIAL", `Parameter Name`== "EC PM2.5 LC TOR", Longitude >= -100) %>% 
  summarise(avg_concentration = mean(`Arithmetic Mean`))



```

## Question 8
Amongst monitoring sites that are labeled as COMMERCIAL for "Land Use", which month of the year has the highest average levels of "Sulfate PM2.5 LC"?

```{r}
library(lubridate`)
joined_tbl %>% 
  group_by(month(`Date Local`)) %>% 
  filter(`Land Use`=="COMMERCIAL", `Parameter Name`=="Sulfate PM2.5 LC") %>% 
  summarise(avg_concentration = mean(`Arithmetic Mean`)) %>% 
  arrange(desc(avg_concentration))
```


## Question 9:
Take a look at the data for the monitoring site identified by State Code 6, County Code 65, and Site Number 8001 (this monitor is in California). At this monitor, for how many days is the sum of "Sulfate PM2.5 LC" and "Total Nitrate PM2.5 LC" greater than 10?

For each of the chemical constituents, there will be some dates that have multiple Sample.Value's at this monitoring site. When there are multiple values on a given date, take the average of the constituent values for that date.

```{r}

joined_tbl %>% 
  filter(`State Code`==6, `County Code`==65, `Site Number`==8001, `Parameter Name` %in% c("Total Nitrate PM2.5 LC", "Sulfate PM2.5 LC")) %>% 
  group_by(`Site Number`, month = month(`Date Local`),`Parameter Name`, day = day(`Date Local`) ) %>% 
  summarise(avg_value = sum(mean(`Arithmetic Mean`))) %>% 
  filter(avg_value > 10) %>% 
  arrange(month,day) 
```


Question 10:

Which monitoring site in the dataset has the highest correlation between "Sulfate PM2.5 LC" and "Total Nitrate PM2.5 LC" across all dates? Identify the monitoring site by it's State, County, and Site Number code.

For each of the chemical constituents, there will be some dates that have multiple Sample.Value's at a monitoring site. When there are multiple values on a given date, take the average of the constituent values for that date.

Correlations between to variables can be computed with the cor() function.

```{r}
joined_tbl %>% 
  filter(`State Code`==6, `County Code`==65, `Site Number`==8001, `Parameter Name` %in% c("Total Nitrate PM2.5 LC", "Sulfate PM2.5 LC")) %>% 
  group_by(`Site Number`, month = month(`Date Local`),day = day(`Date Local`), `Parameter Name` ) %>% 
  summarise(avg_value = mean(`Arithmetic Mean`)) %>% 
  spread(`Parameter Name`, avg_value) %>% 
  summarise(correlation = cor(x=`Total Nitrate PM2.5 LC`, y=`Sulfate PM2.5 LC`, use="pairwise.complete.obs"))
```


```{r}
%>% 
  
```




